---
title: "Seeking_Help"
author: "Anna"
date: '2022-07-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading Help files

R, and every package, provide help files for functions. This will load up a help page in RStudio:

```{r, eval=FALSE}
?function_name
help(function_name)
```

Each help page is broken down into sections (Description, Usage, Arguments etc). The last section Examples is very useful.
The command below will bring up the help for the function `log`.

```{r, eval=FALSE}
?log
```

> ## Tip: Reading help files
>
> One of the most daunting aspects of R is the large number of functions
> available. It would be prohibitive, if not impossible to remember the
> correct usage for every function you use. Luckily, the help files
> mean you don't have to!
{: .callout}
## Special Operators

To seek help on special operators, use quotes:

```{r, eval=FALSE}
?"<-"
```


## When your code doesn't work: seeking help from your peers

If you're having trouble using a function, 9 times out of 10,
the answers you are seeking have already been answered on
[Stack Overflow](http://stackoverflow.com/). 


## Other Resources

* [Quick R](http://www.statmethods.net/)
* [RStudio cheat sheets](http://www.rstudio.com/resources/cheatsheets/)
* [Cookbook for R](http://www.cookbook-r.com/)